Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-12-21 paper/revised-example.tex
Correct bibtex entry

Extending the \agr\ verification results to the system composition
requires additional guarantees not discussed here.  For
example, among other things, contracts for non-synthesized components
must be certified to accurately model their deployed counterparts, the
generated scheduler must be certified to follow the dependent
data-flow in the design, scheduling windows must be certified to cover
worst-case execution times, \etc.  Such additional guarantees are
discussed in other works \cite{gearcase2020, dcrypps2019,
  10.1007/978-3-030-89159-6_18, 10.1007/978-3-030-89159-6_17,
  sel4-2009, scheduled-agree, 9734792}.

>>>>

Extending the \agr\ verification results to the system composition
requires additional guarantees not discussed here.  For
example, among other things, contracts for non-synthesized components
must be certified to accurately model their deployed counterparts, the
generated scheduler must be certified to follow the dependent
data-flow in the design, scheduling windows must be certified to cover
worst-case execution times, \etc.  Such additional guarantees are
discussed in other works \cite{gearcase2020, dcrypps2019,
  10.1007/978-3-030-89159-6_18, 10.1007/978-3-030-89159-6_17,
  sel4-2009, nfm:agree, 9734792}.
